Parallel air palletization and tour planning for simultaneous pickup and delivery

### 2022-11-11 latex/comp_or.tex
SEC_BREAK to secBreak and NCPU to numCpu

An important issue on meta-heuristics is that they are known for the hard work in tuning parameters. For this, when we use the word {\it empirically}\/ throughout the text, we want to say that we accomplished many tests with the hardest instances to fit these values. This does not guarantee best results for all instances, but, on average, overall results are acceptable. Another important observation is that our heuristics were designed based on traditional ideas from the literature \cite{NiarFreville1997,Fidanova2006,Laabadi2018,Alonso2019,Zhan2020} and on the experiences learned during tests.

@@

		\multirow{2}{*}{\textbf{Shims-p}} & $f$              & 5.72        & 3.17        &          &          &          &         &   \\ 
		                                  &{\bf run-time (s)}& 2           & 12          &             &            &            &          &   \\ %299s
		\midrule[.1pt]

		\multirow{2}{*}{\textbf{ACO}}     & $f$              & 5.64        &         &          &        &       &      &   \\ 
                                          &{\bf run-time (s)}& 23          &          &           &        &       &      &   \\ 
        \midrule[.1pt]

        \multirow{2}{*}{\textbf{ACO-p}}   & $f$              & {\bf 5.81}        &         &          &         &       &       &   \\ 
                                          &{\bf run-time (s)}& 16          &           &           &         &       &       &   \\

>>>>

An important issue on meta-heuristics is that they are known for the hard work in tuning parameters. For this, when we use the word {\it empirically}\/ throughout the text, we want to say that we accomplished many tests with the hardest instances to fit these values. This does not guarantee best results for all instances, but, on average, overall results are acceptable. Another important observation is that our heuristics were designed based on traditional ideas from the literature \cite{Fidanova2006} and on the experiences learned during tests.

@@

		\multirow{2}{*}{\textbf{Shims-p}} & $f$              & 5.88        & 3.16        &          &          &          &         &   \\ 
		                                  &{\bf run-time (s)}& 1           & 10          &             &            &            &          &   \\ %299s
		\midrule[.1pt]

		\multirow{2}{*}{\textbf{ACO}}     & $f$              & 5.77        &         &          &        &       &      &   \\ 
                                          &{\bf run-time (s)}& 14          &          &           &        &       &      &   \\ 
        \midrule[.1pt]

        \multirow{2}{*}{\textbf{ACO-p}}   & $f$              & 5.82        &         &          &         &       &       &   \\ 
                                          &{\bf run-time (s)}& 22          &           &           &         &       &       &   \\
